The Three-HITs Theorem\footnote{This work was partially supported by COST Action CA15123.}

### 2017-03-06 Paper/Paper.tex
Added proof that colimits commute with sums (in TeX and Coq code).

For this we use the eliminator of the homotopy colimit.
First, we need to make for all $n$ a map $I^1 \times B_i \> (F \> n)  \rightarrow \hocolim \> F \> f$.
By definition we have the following string of maps
\[
\xymatrix
{
	I^1 \times B_i \> (F \> n) \ar[r]^-{\inn_1} & I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr}& F(n+1) \ar[rr]^-{\inc(n+1)} & & \hocolim \> F \> f.
}
\]
Next we need to show that the following diagram commutes.
\[
\xymatrix
{
	I^1 \times B_i \> (F \> n) \ar[r]^-{\inn_1} \ar[d]_{I^1 \times B_i \> (f \> n)} & I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr} \ar[d]_{I^1 \times B_i \> (f \> n) + f \> n} & F(n+1) \ar[d]^{f(n+1)}\\
	I^1 \times B_i \> (F(n+1)) \ar[r]_-{\inn_1} & I^1 \times B_i \> (F(n+1)) + F(n+1) \ar[r]_-{\inr}& F(n+2) 
}
\]
Note that the left diagram commutes.
For the right diagram we can unpack the definition of $f(n+1)$.
\[
\xymatrix
{
	I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr} \ar[d]_{I^1 \times B_i \> (f \> n) + f \> n} & F(n+1) \ar[d]^{f(n+1)} \ar[dl]^{\inn_2}\\
	I^1 \times B_i \> (F(n+1)) + F(n+1) \ar[r]_-{\inr}& F(n+2) 
}
\]
On the second coordinate it commutes by definition and on the first it commutes by how $F(n+2)$ was defined.

@@

Remaining:
\begin{equation*}
\begin{split}
\com_*(\ap \> (\inc \> n) \> \glue (\inl (0, x))) = \ap \> (\inc (n+1))) \>\glue (\inl (0, f \> n \> x))\\
(\ap \> \overline{t_i} \> \com)^{-1} \conc \ap \> (\inc \> n) \> \glue (\inl (0, x)) \conc \ap \> p_i \> \com
\end{split}
\end{equation*}
$(\ap \> \overline{t_i} \> \com)^{-1}$ is like $\ap \> (\inc \> n) \> (\ap \> c \> \ldots (\ldots \ap \> \text{coherence path}))$, because of the computation rule of $c_i$.

@@

\begin{proof}
We define $f : A \rightarrow \hocolim \> (\lambda n . A) \> (\lambda n . \operatorname{Id})$ to be $\inc \> 0$.
Next we define $g : \hocolim \> (\lambda n . A) \> (\lambda n . \operatorname{Id}) \rightarrow A$ by $\hocolim$ recursion.
We send $\inc \> n \> a$ to $a$, and then the required diagrams commute by reflexivity.
For the proof that it these maps are mutual inverses, we refer the reader to the accompanying Coq code \cite{CoqImpl}.
\end{proof}

\begin{lemma}
\label{lem:colimsum}
Colimits commute with coproducts.
\end{lemma}

>>>>

For this we use the eliminator of the homotopy colimit.
First, we need to make for all $n$ a map $I^1 \times B_i \> (F \> n)  \rightarrow \hocolim \> F \> f$.
By definition we have the following string of maps
\[
\xymatrix
{
	I^1 \times B_i \> (F \> n) \ar[r]^-{\inn_1} & I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr}& F(n+1) \ar[rr]^-{\inc(n+1)} & & \hocolim \> F \> f.
}
\]
Next we need to show that the following diagram commutes.
\[
\xymatrix
{
	I^1 \times B_i \> (F \> n) 
		\ar[r]^-{\inn_1} \ar[d]_{I^1 \times B_i \> (f \> n)} 
	& I^1 \times B_i \> (F \> n) + F \> n 
		\ar[r]^-{\inr} 
		%\ar[d]_{I^1 \times B_i \> (f \> n) + f \> n} 
	& F(n+1) 
		\ar[d]^{f(n+1)}
	\\
	I^1 \times B_i \> (F(n+1)) 
		\ar[r]_-{\inn_1} 
	& I^1 \times B_i \> (F(n+1)) + F(n+1) 
		\ar[r]_-{\inr}
	& F(n+2) 
}
\]
Note that this diagram commutes.
For $x : I^1 \times B_i(F \> n)$ the path is $\glue(\inn_3 \> x)$.
In particular, this means that $\apd \> p_i \> (\com \> n) \equiv \apd \> \inc(n+2) \> \glue(\inn_3 \> x)$
%For the right diagram we can unpack the definition of $f(n+1)$.
%\[
%\xymatrix
%{
%	I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr} \ar[d]_{I^1 \times B_i \> (f \> n) + f \> n} & F(n+1) \ar[d]^{f(n+1)} \ar[dl]^{\inn_2}\\
%	I^1 \times B_i \> (F(n+1)) + F(n+1) \ar[r]_-{\inr}& F(n+2) 
%}
%\]
%On the second coordinate it commutes by definition and on the first it commutes by how $F(n+2)$ was defined.

In order to check that the paths have the right endpoints, we first need to extend the $\overline{t_i} \> n : B_i(F \> n) \rightarrow H_{\Con} (F \> n)$ to a map $B_i(\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
For $n : \mathbb{N}$ and $(y, x) : 2 \times B_i(F \> n)$, we take 
\[
\inc \> (n+1) \> (\inl (g_1 (\inn_1 \> (y, x)))) \equiv \inc \> (n+1) \> (\inl(\overline{t_i} \> n \> (y, x))).
\]
For the image of com we have the following propositional equalities.
\begin{equation*}
\begin{split}
\inc &\> (n+2) \> (\inl(\overline{t_i} \> (n+1) \> (y, f \> n \> x)))
\\
&= \inc \> (n+2) \> ( f \> (n+1) \> (\inl(\overline{t_i} \> n \> (y, x))))
\\
&= \inc \> (n+1) \> (\inl(\overline{t_i} \> n \> (y, x))).
\end{split}
\end{equation*}
The first equation holds by the coherency on the points, and the second by $\com$.

@@

We have
\begin{equation*}
\begin{split}
(\com \> n)_*(\ap \> (\inc \> n) \> \glue (\inl (0, x))) 
&= (\ap \> \overline{t_i} \> (\com \> n))^{-1} \conc \ap \> (\inc \> n) \> \glue (\inl (0, x)) \conc \ap \> p_i \> (\com \> n)\\
= \ap \> (\inc (n+1))) \>\glue (\inl (0, f \> n \> x))\\
\end{split}
\end{equation*}
$(\ap \> \overline{t_i} \> \com)^{-1}$ is like $\ap \> (\inc \> n) \> (\ap \> c \> \ldots (\ldots \ap \> \text{coherence path}))$, because of the computation rule of $c_i$.

@@

\begin{proof}
We define $f : A \rightarrow \hocolim \> (\lambda n . A) \> (\lambda n . \operatorname{Id})$ to be $\inc \> 0$.
Next we define $g : \hocolim \> (\lambda n . A) \> (\lambda n . \operatorname{Id}) \rightarrow A$ by $\hocolim$ recursion.
We send $\inc \> n \> a$ to $a$, and then the required diagrams commute by reflexivity.
The proof that these maps are mutual inverses is straightforward but tedious, so we refer the reader to the accompanying Coq code \cite{CoqImpl}.
\end{proof}

\begin{lemma}
\label{lem:colimsum}
Colimits commute with coproducts, so $\hocolim \> ((G_1 + G_2) \circ F) \> ((G_1 + G_2) \> f)$ and $\hocolim \> (G_1 \circ F) \> (G_1 \> f) + \hocolim \> (G_2 \circ F) \> (gG2 \> f)$ are isomorphic.. 
\end{lemma}

\begin{proof}
This one is not difficult either, so we will be brief and refer the reader to \cite{CoqImpl} for details.
We start by making a map 
\[
\hocolim \> ((G_1 + G_2) \circ F) \> ((G_1 + G_2) \> f) \rightarrow \hocolim \> (G_1 \circ F) \> (G_1 \> f) + \hocolim \> (G_2 \circ F) \> (G_2 \> f).
\]
This map is defined by recursion over the colimit, so take any $n : \mathbb{N}$ and $x : F \> n$.
Then the image of $\inc \> n \> (\inn_i \> x)$ is defined to be $\inn_i (\inc \> n \> x)$, and the image of $\com \> n \> (\inn_i \> x)$ is defined by
$\ap \> \inn_i \> (\com \> (G1 \circ F) \> (G_1 \> f) \> n \> x)$.

For the map in the other direction, we need to make 
\[
\hocolim \> (G_i \circ F) \> (G_i \> f) \rightarrow \hocolim \> ((G_1 + G_2) \circ F) \> ((G_1 + G_2) \> f).
\]
We send $\inc \> n \> x$ to $\inc \> n \> (\inn_i \> x)$ and $\com \> n \> x$ to $\com \> n \> (\inn_i \> x)$.
\end{proof}
